JD notes on effects

### 2022-07-29 manuscript/body.tex
Editing discussion

The argument and results we present in this paper support a greater need for a shift in focus on how to summarize these kinds of models. From our theoretical, methodological and simulation results, researchers using these models should, in the absence of theoretical justification, report predictions based on the observed-value-based approach or at least attempt to compare the two approaches before settling on the most appropriate in answering their research question. Moreover, we provide \proglang{R} package, \pkg{vareffects}, which implements these methods and is available on GitHub (\href{https://github.com/mac-theobio/effects}{https://github.com/mac-theobio/effects}).

>>>>

The argument and results we present in this paper support a greater need for a shift in focus on how to summarize these kinds of models. From our theoretical, methodological and simulation results, researchers using these models should, in the absence of theoretical justification, report predictions based on the observed-value approach or at least attempt to compare the two approaches before settling on the most appropriate in answering their research question. Moreover, we provide \proglang{R} package, \pkg{vareffects}, which implements these methods and is available on GitHub (\href{https://github.com/mac-theobio/effects}{https://github.com/mac-theobio/effects}).
